---
title: "Project 3"
author: "Alain T Kuiete"
date: "10/17/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
```

### Data Science Skills

#### Data Science General Skills

##### Downloading data
```{r}
dsg <- read.csv("https://raw.githubusercontent.com/AlainKuiete/DATA607/master/ds_general_skills_revised.csv" )
str(dsg)
```

#### Subsetting the Data Science soft Skills 
```{r}
dskg <-dsg[1:15,]
```

#### reshaping my dataframe
```{r}
colnames(dskg) <- c("D.Skills", "LinkedIn", "Indeed", "SimplyHired", "Monster")
dskg$LinkedIn <- as.numeric(gsub(",","",dskg$LinkedIn))
dskg$Indeed <- as.numeric(gsub(",","",dskg$Indeed))
dskg$SimplyHired <- as.numeric(gsub(",","",dskg$SimplyHired))
dskg$Monster <- as.numeric(gsub(",","",dskg$Monster))
```


#### Computation
```{r}
s.dskg <- summarise(dskg, sL=sum(LinkedIn, na.rm=TRUE), sI= sum(Indeed, na.rm=TRUE), sS=sum(SimplyHired, na.rm=TRUE),
           sM=sum(Monster, na.rm=TRUE))

tsg <- sum(s.dskg)

g.skills <- dskg%>% mutate(D.Skills, pct=(LinkedIn+Indeed+SimplyHired+Monster)/tsg)%>%
  select(D.Skills,pct)
g.skills
```

##### Changing the values of variable D.skill
```{r}
D.Skills.abv <-c("ml", "an", "st", "cs", "co", "ma", "vi","ai",
                     "dl","nlp", "sd", "nn", "de", "pm","se")
g.skild <- data.frame(g.skills,
                      ds.abv = D.Skills.abv,
                      D.Skills = g.skills$D.Skills,
                      pct=g.skills$pct)

```

#### Visualisation

```{r}
ggplot(g.skild, 
       aes(x=ds.abv, y = pct))+
  geom_col(aes(fill=D.Skills), position = "dodge")+
  xlab("Genaral Skills")+ylab("Overall percentage")+
  ggtitle("General Skills for Data Science")
```

#### Analysis, Machine Learning, Statistics, Computer Science and Communication are general skill required for Data Scientists.



#### Data Science Soft Skills

##### Downloading data
```{r}
dss <- read.csv("https://raw.githubusercontent.com/AlainKuiete/DATA607/master/ds_job_listing_software.csv")
```


#### Subsetting the Data Science soft Skills 
```{r}
dsk <- dss[1:30,1:5]
str(dsk)
```

#### reshaping my dataframe
```{r}
colnames(dsk) <- c("D.Skills", "LinkedIn", "Indeed", "SimplyHired", "Monster")
dsk$LinkedIn <- as.numeric(gsub(",","",dsk$LinkedIn))
dsk$Indeed <- as.numeric(gsub(",","",dsk$Indeed))
dsk$SimplyHired <- as.numeric(gsub(",","",dsk$SimplyHired))
dsk$Monster <- as.numeric(gsub(",","",dsk$Monster))
```


#### Computation
```{r}
s.dsks <- summarise(dsk, sL=sum(LinkedIn), sI= sum(Indeed), sS=sum(SimplyHired),
           sM=sum(Monster))
ts <- sum(s.dsks)

skills <- dsk%>% mutate(D.Skills, pct=(LinkedIn+Indeed+SimplyHired+Monster)/ts)%>%select(D.Skills,pct)
skill <-skills[1:10,]
skill
```



#### Visualisation
```{r}
ggplot(skill, 
       aes(x=D.Skills, y = pct))+ 
  geom_col(aes(fill=D.Skills), position = "dodge")+
  xlab("Computer Skills")+ylab("Overall percentage")+
  ggtitle("Top 10 Sofware Skills for Data Science")
```

### Python and R are the most software computer skills recommanded for Data Scientist.


##### Reference: The Most in Demand Skills for Data Scientists by Jeff Hale. Toward Data Science
